---
title: "NFHS ARI Table 2"
author: "Hector"
date: '2022-06-27'
output: word_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
knitr::opts_chunk$set(echo = FALSE)

library(tidyverse)   # data management + ggplot2 graphics
library(survey)      # for survey functions
library(srvyr)       # dplyr wrapper for survey package
library(gtsummary)   # wrapper for survey package to produce tables

library(table1)
library(labelled) # Contains the look_for() function
library(epiDisplay) # tab1()
```

## Merging the datasets

```{r}
nfhs4 <- readRDS("nfhs4_ari.Rds")
nfhs5 <- readRDS("nfhs5_ari.Rds")

nfhs4 <- nfhs4 %>% mutate(wave = "NFHS4")
nfhs5 <- nfhs5 %>% mutate(wave = "NFHS5")

nfhs <- bind_rows(nfhs4, nfhs5)

```

## Loading the dataset
```{r}
write_rds(nfhs,"nfhs_ari_all.Rds")
nfhs <- read_rds("nfhs_ari_all.Rds")
```


## Weights and survey design

```{r}
nfhs <- nfhs %>% 
  mutate(wgt = v005/1000000) %>%  # Turning wewights into decimals
  mutate(strata = as.character(paste(nfhs$state_f, nfhs$place_f, sep = " "))) # Strata based on region and urban/rural
tab1(nfhs$strata)
nfhs_design <- nfhs4 %>%
  as_survey_design(ids = v001, # cluster ids
                   weights = wgt, # weight variable created above
                   strata = strata, # strata
                   nest = TRUE,
                   check.strata = TRUE
                  )
```

```{r}
options(survey.lonely.psu="certainty")
```

## Table 2. Descriptive analysis by strata

```{r}
theme_gtsummary_compact(set_theme = TRUE, font_size = NULL)
table1 <- nfhs_design %>%
  tbl_svysummary(
    by = place_f,
    missing_text = "Missing",
    type = list(all_continuous() ~ "continuous",
                all_categorical() ~ "categorical"),
    statistic = list(all_continuous() ~ "{mean} (+/-{sd})",
                     all_categorical() ~ "{n} ({p}%)",
                     all_dichotomous() ~ "{n} ({p}%)"),
    digits = list(all_continuous() ~ c(1, 1),
                  all_categorical() ~ c(0, 1),
                  all_dichotomous() ~ c(1, 1)),
    
    include = c(
# Demographics
                   
# Treatment related variables
source_g1_f,
days.after_g_f,
eat_g_f,
drink_g_f),
    label = c(
# Treatment related variables
source_g1_f ~ "Source of treatment",
days.after_g_f ~ "Days after treatment",
eat_g_f ~ "Amount given to eat",
drink_g_f ~ "Amount given to drink")) %>% 
  add_overall() %>% 
  modify_header(c(stat_1, stat_2) ~ "**{level}**<br>N = {n} ({style_percent(p, digits = 1)}%)") %>%
  bold_labels() %>% 
  modify_header(label ~ "") %>%
  modify_footnote(
    all_stat_cols() ~ "Mean (SD) or Frequency (%)")

table1_flex <- as_flex_table(table1)
table1_flex
```

## Table 2. Descriptive analysis by outcome


theme_gtsummary_compact(set_theme = TRUE, font_size = NULL)
table1 <- survey_design %>%
  tbl_strata(
    strata = place_f,
    .tbl_fun =
      ~ .x %>% 
  tbl_svysummary(
    by = antibiotics_f,
    missing_text = "Missing",
    type = list(all_continuous() ~ "continuous",
                all_categorical() ~ "categorical"),
    statistic = list(all_continuous() ~ "{mean} (+/-{sd})",
                     all_categorical() ~ "{n} ({p}%)",
                     all_dichotomous() ~ "{n} ({p}%)"),
    digits = list(all_continuous() ~ c(1, 1),
                  all_categorical() ~ c(0, 1),
                  all_dichotomous() ~ c(1, 1)),
    
    include = c(
# Demographics
                   
# Treatment related variables
source_g1_f,
days.after_g_f,
eat_g_f,
drink_g_f),
    label = c(
# Treatment related variables
source_g1_f ~ "Source of treatment",
days.after_g_f ~ "Days after treatment",
eat_g_f ~ "Amount given to eat",
drink_g_f ~ "Amount given to drink")) %>% 
  add_overall() %>% 
  modify_header(c(stat_1, stat_2) ~ "**{level}**<br>N = {n} ({style_percent(p, digits = 1)}%)") %>%
  bold_labels() %>% 
  modify_header(label ~ "") %>%
  modify_footnote(
    all_stat_cols() ~ "Mean (SD) or Frequency (%)"))

table1_flex <- as_flex_table(table1)
table1_flex