---
title: "NFHS4 Data cleaning"
author: "Hector"
date: '2022-05-18'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# NFHS4 Data cleaning

## Objectives

-   Input the dataset from .DTA file.

-   Create a .R dataset easier and quicker to handle.

-   Reduce the number of obs. to children <60 months (original selection, in the recoding file we selected for <36 months)

-   Delete variables containing all NA's values.


### Loading the dataset

First of all we will load the necessary packages:

```{r}
library(tidyverse)
library(labelled) # Contains the look_for() function
library(epiDisplay) # tab1()
```

Due to the big size of the .DTA we need to push the RAM memory by doing garbage collection (RAM memory cleaning) and raising the memory.limit:
```{r}
gc()
memory.limit()
memory.limit(size = 30000)
```

Then we will proceed to load the NFHS dataset onto R.

```{r}
library(haven)
IABR73FL <- read_dta("IABR73FL.DTA")
```

Saving as R data file, for faster loading.

```{r}
saveRDS(IABR73FL, file = "IABR73FL.Rds")
nfhs4 <- readRDS(file = "IABR73FL.Rds")
```

Selecting only the rows corresponding to U5 children and saving the new dataset:

B19:	 	 	Age of child, or months since birth for children who have died, in completed months, computed as: B19 = int( (V008A - B18) / 30.4375)

503  b8       current age of child                                       dbl 
824  hw1      na - child's age in months                                 dbl    

498 b3       date of birth (cmc)                                     dbl
11  v008     date of interview (cmc)                                 dbl   

First we need to create the age variable by subtracting the date of birth of the child (CMC) to the date of the interview (CMC)
```{r}
nfhs4 <- nfhs4 %>% 
  mutate(age.years = as.integer((v008 - b3)/12 )) %>% 
  mutate(age = v008 - b3)

```

Creating a .Rds file with only children less than 5 years old

```{r}
nfhs4short <- nfhs4 %>% filter(age < 60)
saveRDS(nfhs4short, file = "IABR73FL_under5.Rds")
```

Loading a function for selecting all columns that does not contain all NAs.
```{r}
not_all_na <- function(x) any(!is.na(x))

nfhs4shorter <- nfhs4short %>% select_if(not_all_na)
```

Saving the resulted dataset:

```{r}
saveRDS(nfhs4shorter, file = "IABR73FL_under5_short.Rds")
```

Checking the age distribution to corroborate the selection:

```{r}
tab1(nfhs4shorter$age.years)
tab1(nfhs4shorter$age)
```
