---
title: "NFHS Analysis Table 1"
author: "Hector"
date: '2022-05-27'
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# NFHS Analysis Table 1 unweighted

## Objective

- To create a table 1 desvribing the different predictor variables and containing the Mean (SD/SE) for continuous variables and Frequency (%) for categorical/dichotomous variables.

Table S2 containing unweighted treatment variables was originally included in table 1 and separated manually into table S2.

The `table1` package can do this with the unweighted data. For the weighted data we will use the `gtsummary` package.

```{r}
knitr::opts_chunk$set(echo = FALSE)

library(tidyverse)   # data management + ggplot2 graphics
library(tsibble)     # handle time series datasets
library(survey)      # for survey functions
library(srvyr)       # dplyr wrapper for survey package
library(gtsummary)   # wrapper for survey package to produce tables

library(table1)
library(labelled) # Contains the look_for() function
library(epiDisplay) # tab1()
```

## Merging the datasets

```{r}
nfhs4 <- readRDS("nfhs4_ari.Rds")
nfhs5 <- readRDS("nfhs5_ari.Rds")

nfhs4 <- nfhs4 %>% mutate(wave = "NFHS4")
nfhs5 <- nfhs5 %>% mutate(wave = "NFHS5")

nfhs <- bind_rows(nfhs4, nfhs5)

```

## Loading the dataset
```{r}
write_rds(nfhs,"nfhs_ari_all.Rds")
nfhs <- read_rds("nfhs_ari_all.Rds")
```

## Table 1. Descriptive analysis.

Analysis of our target population kids with ARI (N = 16972)

There are two ways of using the function `table1()` either as a formula or listing the variables and the strata.

It is important to label correctly the different variables with the names that are appearing at the table. Also for levels of categorical variables.

```{r}
label(nfhs$sex_f) <- "Sex"
label(nfhs$age) <- "Age"
units(nfhs$age) <- "months"
```

Formula structure:

table1(~ var1 + var2 + var3 | place_f*antibiotics_f, data=nfhs)

Listing structure and re-labelling factor variables:

```{r}
attach(nfhs)
nfhs$antibiotics_f <- factor(antibiotics_f, labels = c("No", "Yes"))
nfhs$handwash.soap_f <- factor(handwash.soap_f, labels = c("No", "Yes"))
nfhs$visit3mo_f <- factor(visit3mo_f, labels = c("No", "Yes"))
nfhs$insurance_f <- factor(insurance_f, labels = c("No", "Yes"))
nfhs$icds_f <- factor(icds_f, labels = c("No", "Yes"))
nfhs$wi_f <- factor(wi_f, labels = c("Poorest", "Poorer", "Middle", "Richer", "Richest"))
nfhs$sex_f <- factor(sex_f, labels = c("Male", "Female"))
nfhs$media_f <- factor(media_f, 
                         labels = c("Not at all", "Less than once a week", 
                                   "At least once a week", "Almost every day"))
detach(nfhs)
```
            
## Table 1 NFHS merged by urban/rural.

```{r}
labels <- list(
    variables=list(# Outcome variables
      
                   antibiotics_f = "Were given antibiotics",
                   
                   # Demographics
                   wi_f = "Wealth index",
                   religion_f = "Religion",
                   caste_f = "Caste/Tribe",
      
                   # Mother's associated variables
                   m.age = "Mother's age (years)",
                   m.edu.att_f = "Educational level",
                   
                   # Household variables
                   hhsize = "Household size",
                   died_f = "Prior children deceased",
                   fuel_g_f = "Type of cooking fuel",
                   water.source_g_f = "Source of drinking water",
                   toilet_g_f = "Toilet facility",
                   handwash.soap_f = "Soap for handwashing",
                   media_f = "Media accessibility",
                   bpl_f = "Below Poverty Line card",
                   smoke_g_f = "Smoke exposure",
                   
                   # Child related variables
                   age = "Age (months)",
                   sex_f = "Sex",
                   bord = "Birth order",
                   delivery_g_f = "Place of delivery",
                   stunting_g_f = "Stunting (height/age)",
                   wasting_g_f = "Wasting (weight/height)",
                   
                   # Health care related variables
                   access = "Problems accessing healthcare",
                   visit3mo_f = "Health worker visit in last 3 months",
                   insurance_f = "Covered by health insurance",
                   healthcard_f = "Vaccination card",
                   fimm_f = "Fully immunized",
                   icds_f = "Anganwadi or ICDS benefits",
                   parasites_f = "Drugs for intestinal parasites (last 6 months)",
                   vitA_f = "Vitamin A supplementation (last 6 months)",
                   iron_f = "Iron supplementation (last 7 days)",
                   
                   # Treatment related variables
                   source_g1_f = "Source of treatment",
                   days.after = "Days after treatment",
                   eat_g_f = "Amount given to eat",
                   drink_g_f = "Amount given to drink"
                   ))

strata <- c(list(Total=nfhs),
            list("Urban"=subset(nfhs, place_f == "Urban")),
            list("Rural"=subset(nfhs, place_f == "Rural")))
```


## Custom render

Table1 allows to customize the contents using custom renderers. A custom render can be a function that take a vector as the first argument and return a (named) character vector. There is also a simpler way to customize the table contents using an abbreviated code syntax instead of a render function, but it allows less control over rounding (see below). Here, for example, we specify render functions for the continuous and categorical variables as follows:

```{r}
my.render.cont <- function(x) {
    with(stats.apply.rounding(stats.default(x), digits=3), c("",
        "Mean (SD)"=sprintf("%s (&plusmn; %s)", MEAN, SD)))
}
my.render.cat <- function(x) {
    c("", sapply(stats.default(x), function(y) with(y,
        sprintf("%d (%.1f%%)", FREQ, PCT))))
}

```



```{r}
table1(strata, labels,
       render.continuous=my.render.cont, render.categorical=my.render.cat)
```
## Table 1 by urban/rural and wave.

```{r}
labels <- list(
    variables=list(# Outcome variables
                   antibiotics_f = "Were given antibiotics",
                   
                   # Demographics
                   state_f = "State",
                   wi_f = "Wealth index",
                   religion_f = "Religion",
                   caste_f = "Caste/Tribe",
                   
                   # Child related variables
                   sex_f = "Sex",
                   age = "Age (months)",
                   bord = "Birth order",
                   bord_f = "Birth order cat",
                   delivery_g_f = "Place of delivery",
                   interview.quarter_f = "Interview season",
                   breastfed_g_f = "Breastfeeding",
                   stunting_g_f = "Stunting (height/age)",
                   wasting_g_f = "Wasting (weight/height)",
                   
                   # Mother's associated variables
                   m.age = "Mother's age",
                   mageb_g_f = "Maternal age at child birth \u2265 20",
                   m.edu.att_f = "Educational level",
                   m.tobacco_f = "Tobacco consumption",
                   smoke_g_f = "Smoke exposure",
                   
                   # Household variables
                   hhsize = "Household size",
                   fuel_g_f = "Type of cooking fuel",
                   water.source_g_f = "Source of drinking water",
                   toilet_g_f = "Toilet facility",
                   handwash.soap_f = "Soap for handwashing",
                   media_f = "Media accessibility",
                   bpl_f = "Below Poverty Line card",
                   
                   # Treatment related variables
                   source_g1_f = "Source of treatment",
                   days.after = "Days after treatment",
                   days.after_f = "Days after treatment cat",
                   eat_g_f = "Amount given to eat",
                   drink_g_f = "Amount given to drink",
                   
                   # Health care related variables
                   access = "Problems accessing healthcare",
                   distance_f = "Distance to health facility",
                   visit3mo_f = "Health worker visit in last 3 months",
                   insurance_f = "Covered by health insurance",
                   healthcard_f = "Has health card",
                   
                   # Vaccination
                   fimm_f = "Fully immunized",
                   dpt3 = "DPT vaccine (3 doses)",
                   polio3 = "Polio (3 doses)",
                   bcg_f = "BCG vaccine",
                   measles_f = "Measles vaccine",
                   
                   icds_f = "Anganwadi or ICDS benefits",
                   parasites_f = "Drugs for intestinal parasites (last 6 months)",
                   vitA_f = "Vitamin A supplementation (last 6 months)",
                   iron_f = "Iron supplementation (last 7 days)"
                   ),
groups = list("NFHS4", "NFHS5", ""))

strata <- c(list("Urban"=subset(nfhs, place_f == "Urban" & wave == "NFHS4")),
            list("Rural"=subset(nfhs, place_f == "Rural" & wave == "NFHS4")),
            list("Urban"=subset(nfhs, place_f == "Urban" & wave == "NFHS5")),
            list("Rural"=subset(nfhs, place_f == "Rural" & wave == "NFHS5")),
            list(Total=nfhs))
```

### Table 1 with only continuous variables.

```{r}
labels <- list(
    variables=list(# Outcome variables
                   antibiotics_f = "Were given antibiotics",
                   age = "Age (months)",
                   # Mother's associated variables
                   m.age = "Mother's age (years)",
                   # Household variables
                   hhsize = "Household size",
                   # Health care related variables
                   access = "Problems accessing healthcare"
                   ))

strata <- c(list(Total=nfhs),
            list("Urban"=subset(nfhs, place_f == "Urban")),
            list("Rural"=subset(nfhs, place_f == "Rural")))
```


## Custom render continuous

```{r}
my.render.cont <- function(x) {
    with(stats.apply.rounding(stats.default(x), digits=3), c("",
        "Mean (SD)"=sprintf("%s (&plusmn; %s, %s)", MEAN, SD, N)))
}
my.render.cat <- function(x) {
    c("", sapply(stats.default(x), function(y) with(y,
        sprintf("%d (%.f%%)", FREQ, PCT))))
}
```

```{r}
table1(strata, labels,
       render.continuous=my.render.cont, render.categorical=my.render.cat)
```
After several attempts I did not manage to add the SE instead of the SD to the `table1()` function so I calculated and changed them manually:

```{r}

library(plotrix)
std_mean <- function(x) sd(x)/sqrt(length(x))
se_urban <- function(sd) sd/sqrt(3402)
se_rural <- function(sd) sd/sqrt(13570)
se_abx <- function(sd) sd/sqrt(3266)

se_abx(2.7)

std_mean(nfhs$bord)
se_urban(4.62)
se_rural(4.83)

std_mean(nfhs$age)
se_urban(4.62)
se_rural(4.83)

std_mean(nfhs$m.age)
se_urban(4.62)
se_rural(4.83)

std_mean(nfhs$hhsize)
se_urban(2.82)
se_rural(2.79)

std_mean(nfhs$access)
se_urban(4.62)
se_rural(4.83)

```

