---
title: "NFHS5 HH cleaning"
author: "Hector"
date: '2022-05-18'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Loading the dataset

First of all we will load the necessary packages:

```{r}
library(tidyverse)
library(labelled) # Contains the look_for() function
library(epiDisplay) # tab1()
```


Pushing a bit the RAM memory by doing garbage collection (RAM memory cleaning) and raising the memory.limit:
```{r}
gc()
memory.limit()
memory.limit(size = 100000)
```

Then we will proceed to load the NFHS dataset onto R.

```{r}
library(haven)
#hhsurvey5 <- read_dta("IAHR7AFL.DTA")
```

### Save as R data file, for faster loading.

```{r}
#saveRDS(hhsurvey5, file = "IAHR7AFL.Rds")

hhsurvey5 <- readRDS(file = "IAHR7AFL.Rds")
```

Selecting only the variables necessary for merging and washing hands:

 63  hv230a   place where household members wash their hands dbl+lbl  [1] observed                          
                                                                      [2] not observed: not in dwelling     
                                                                      [3] not observed: no permission to see
                                                                      [4] not observed: other reason        
 64  hv230b   presence of water at hand washing place        dbl+lbl  [0] water not available               




```{r}
hhsurvey5_small <- hhsurvey5 %>% dplyr::select(hhid, hv000, hv001, hv002, hv003, hv004, hv005, hv230a, hv230b, hv232, hv232b, hv232y, hv252, sh75)
```


Saving the resulted dataset:

```{r}
saveRDS(hhsurvey5_small, file = "hhsurvey5_small_merge.Rds")
```
