---
title: "NFHS ARI Table 2"
author: "Hector"
date: '2022-06-27'
output: word_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# NFHS Analysis Table 1 weighted

## Objectives

- To create a table containing the Mean (SD/SE) for continuous variables and Frequency (%) for categorical/dichotomous variables.

- Table 2 with weighted data describing the treatment-related variables.

For the weighted data we will use the `gtsummary` package.

### Loading packages

```{r}
knitr::opts_chunk$set(echo = FALSE)

library(tidyverse)   # data management + ggplot2 graphics
library(survey)      # for survey functions
library(srvyr)       # dplyr wrapper for survey package
library(gtsummary)   # wrapper for survey package to produce tables

library(labelled) # Contains the look_for() function
library(epiDisplay) # tab1()
```

## Merging the datasets

```{r}
nfhs4 <- readRDS("nfhs4_ari.Rds")
nfhs5 <- readRDS("nfhs5_ari.Rds")

nfhs4 <- nfhs4 %>% mutate(wave = "NFHS4")
nfhs5 <- nfhs5 %>% mutate(wave = "NFHS5")

nfhs <- bind_rows(nfhs4, nfhs5)

```

## Loading the dataset
```{r}
write_rds(nfhs,"nfhs_ari_all.Rds")
nfhs <- read_rds("nfhs_ari_all.Rds")
```


## Weights and survey design

```{r}
nfhs <- nfhs %>% 
  mutate(wgt = v005/1000000) %>%  # Turning wewights into decimals
  mutate(strata = as.character(paste(nfhs$state_f, nfhs$place_f, sep = " "))) # Strata based on region and urban/rural
nfhs$days.after <- labelled::unlabelled(nfhs$days.after)
nfhs_design <- nfhs %>%
  as_survey_design(ids = v001, # cluster ids
                   weights = wgt, # weight variable created above
                   strata = strata, # strata
                   nest = TRUE,
                   check.strata = TRUE
                  )
```

Treating single PSUs as 'Certainty': a single-PSU stratum makes no contribution to the variance (for multistage sampling it makes no contribution at that level of sampling). This is an alternative to specifying fpc, and might be useful for compatibility with other software. 

```{r}
options(survey.lonely.psu="certainty")
```

## Table 2. Descriptive analysis by urban/rural

```{r}
theme_gtsummary_compact(set_theme = TRUE, font_size = NULL)


table1 <- nfhs_design %>%
    mutate_if(is.factor,
            fct_explicit_na,
            na_level = "Missing") %>%  ### Setting missing variables as a category to obtain percentage of missing values
  tbl_svysummary(
    by = place_f,
    missing_text = "Missing",
    type = list(all_continuous() ~ "continuous",
                all_categorical() ~ "categorical",
                days.after ~ "continuous"),
    statistic = list(all_continuous() ~ "{mean} (+/-{sd})",
                     all_categorical() ~ "{n} ({p}%)",
                     all_dichotomous() ~ "{n} ({p}%)"),
    digits = list(all_continuous() ~ c(1, 1),
                  all_categorical() ~ c(0, 1),
                  all_dichotomous() ~ c(1, 1)),
    
    include = c(
# Demographics
                   
# Treatment related variables
source_g1_f,
days.after,
eat_g_f,
drink_g_f),
    label = c(
# Treatment related variables
source_g1_f ~ "Source of treatment",
days.after ~ "Days after treatment",
eat_g_f ~ "Amount given to eat",
drink_g_f ~ "Amount given to drink")) %>% 
  add_overall() %>% 
  modify_header(c(stat_1, stat_2) ~ "**{level}**<br>N = {n} ({style_percent(p, digits = 1)}%)") %>%
  bold_labels() %>% 
  modify_header(label ~ "") %>%
  modify_footnote(
    all_stat_cols() ~ "Mean (SD) or Frequency (%)")

table1_flex <- as_flex_table(table1)
table1_flex
```

## Table 2. Descriptive analysis by outcome

```{r}
theme_gtsummary_compact(set_theme = TRUE, font_size = NULL)
table2 <- nfhs_design %>%
  tbl_strata(
    strata = place_f,
    .tbl_fun =
      ~ .x %>% 
  tbl_svysummary(
    by = antibiotics_f,
    missing_text = "Missing",
    type = list(all_continuous() ~ "continuous",
                all_categorical() ~ "categorical"),
    statistic = list(all_continuous() ~ "{mean} (+/-{sd})",
                     all_categorical() ~ "{n} ({p}%)",
                     all_dichotomous() ~ "{n} ({p}%)"),
    digits = list(all_continuous() ~ c(1, 1),
                  all_categorical() ~ c(0, 1),
                  all_dichotomous() ~ c(1, 1)),
    
    include = c(
# Demographics
                   
# Treatment related variables
source_g1_f,
days.after_g_f,
eat_g_f,
drink_g_f),
    label = c(
# Treatment related variables
source_g1_f ~ "Source of treatment",
days.after_g_f ~ "Days after treatment",
eat_g_f ~ "Amount given to eat",
drink_g_f ~ "Amount given to drink")) %>% 
  add_overall() %>% 
  modify_header(c(stat_1, stat_2) ~ "**{level}**<br>N = {n} ({style_percent(p, digits = 1)}%)") %>%
  bold_labels() %>% 
  modify_header(label ~ "") %>%
  modify_footnote(
    all_stat_cols() ~ "Mean (SD) or Frequency (%)"))

table2_flex <- as_flex_table(table2)
table2_flex
```