---
title: "NFHS5 Cleaning"
author: "Hector"
date: '2022-05-20'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# nfhs5 Data cleaning

## Objectives

-   Input the dataset.

-   Reduce the number of obs. to children <60 months.

-   Delete variables containing all NA's values


### Loading the dataset

First of all we will load the necessary packages:

```{r}
library(tidyverse)
library(labelled) # Contains the look_for() function
library(epiDisplay) # tab1()
```


Pushing a bit the RAM memory by doing garbage collection (RAM memory cleaning) and raising the memory.limit:
```{r}
gc()
memory.limit()
memory.limit(size = 60000)
```

Then we will proceed to load the NFHS dataset onto R.

```{r}
library(haven)
IABR7AFL <- read_dta("IABR7AFL.DTA")

```

Save as R data file, for faster loading.

```{r}
saveRDS(IABR7AFL, file = "IABR7AFL.Rds")
nfhs5 <- readRDS(file = "IABR7AFL.Rds")
```

Selecting only the rows corresponding to U5 children and saving the new dataset:

B19:	 	 	Age of child, or months since birth for children who have died, in completed months, computed as: B19 = int( (V008A - B18) / 30.4375)

503  b8       current age of child                                       dbl 
824  hw1      na - child's age in months                                 dbl    

498 b3       date of birth (cmc)                                     dbl
11  v008     date of interview (cmc)                                 dbl   


```{r}
nfhs5short <- nfhs5 %>% 
  filter(b19 < 60) %>% 
  rename(age = b19)
saveRDS(nfhs5short, file = "IABR7AFL_under5.Rds")

```


Loading a function for selecting all columns that does not contain all NAs.
```{r}
not_all_na <- function(x) any(!is.na(x))

nfhs5shorter <- nfhs5short %>% select_if(not_all_na)
```

Saving the resulted dataset:

```{r}
saveRDS(nfhs5shorter, file = "IABR7AFL_under5_short.Rds")
```


```{r}
tab1(nfhs5shorter$age)
```