---
title: "Regional Analysis"
author: "Hector"
date: '2022-06-22'
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Regional Analysis

## Objectives

- To calculate prevalence of antibiotic consumption in U3 children with ARI by zones and state/union territories.

- To create a table containing the prevalence by zone and state.

- To create a .csv with zone/state name and percentage to use it in QGIS and generate a map graded by prevalence.

- To create a plot with prevalence and 95% CIs by zones and by state.


```{r}
knitr::opts_chunk$set(echo = FALSE)

library(tidyverse)   # data management + ggplot2 graphics
library(survey)      # for survey functions
library(srvyr)       # dplyr wrapper for survey package
library(gtsummary)   # wrapper for survey package to produce tables

library(table1)
library(labelled) # Contains the look_for() function
library(epiDisplay) # tab1()
library(glue)
library(grDevices) # greek letter
```

## Loading datasets
```{r}
nfhs4 <- readRDS("nfhs4_ari.Rds")
nfhs5 <- readRDS("nfhs5_ari.Rds")

nfhs <- bind_rows(nfhs4, nfhs5)
look_for(nfhs,"state")
```

Creating zones variable grouping states by zones to raise sample size.
```{r}
nfhs <- nfhs %>% 
  mutate(zones = case_when(
    state == 1 ~ 1, # Southern
    state == 2 ~ 1,
    state == 3 ~ 6, # Northern Eastern
    state == 4 ~ 6,
    state == 5 ~ 5, # Eastern
    state == 6 ~ 3, # Northern
    state == 7 ~ 4, # Central
    state == 8 ~ 2, # Western
    state == 9 ~ 2,
    state == 10 ~ 1,
    state == 11 ~ 2,
    state == 12 ~ 3,
    state == 13 ~ 3,
    state == 14 ~ 3,
    state == 15 ~ 5,
    state == 16 ~ 1,
    state == 17 ~ 1,
    state == 18 ~ 1,
    state == 19 ~ 4,
    state == 20 ~ 2,
    state == 21 ~ 6,
    state == 22 ~ 6,
    state == 23 ~ 6,
    state == 24 ~ 6,
    state == 25 ~ 3,
    state == 26 ~ 5,
    state == 27 ~ 1,
    state == 28 ~ 3,
    state == 29 ~ 3,
    state == 30 ~ 6,
    state == 31 ~ 1,
    state == 32 ~ 6,
    state == 33 ~ 4,
    state == 34 ~ 4,
    state == 35 ~ 5,
    state == 36 ~ 1,
    state == 37 ~ 1
  )) %>% 
  mutate(zones_f = factor(zones, c(1:6), c("Southern","Western","Northern", "Central", "Eastern", "Northern Eastern") ))
```

## Weights and survey design

```{r}
nfhs4 <- nfhs4 %>% 
  mutate(wgt = v005/1000000) %>%  # Turning weights into decimals
  mutate(strata = as.character(paste(nfhs4$state_f, nfhs4$place_f, sep = " "))) # Strata based on region and urban/rural

nfhs4_design <- nfhs4 %>%
  as_survey_design(ids = v001, # cluster ids
                   weights = wgt, # weight variable created above
                   strata = strata, # strata
                   nest = TRUE,
                   check.strata = TRUE
                  )
```

```{r}
nfhs5 <- nfhs5 %>% 
  mutate(wgt = v005/1000000) %>%  # Turning wewights into decimals
  mutate(strata = as.character(paste(nfhs5$state_f, nfhs5$place_f, sep = " "))) # Strata based on region and urban/rural

nfhs5_design <- nfhs5 %>%
  as_survey_design(ids = v001, # cluster ids
                   weights = wgt, # weight variable created above
                   strata = strata, # strata
                   nest = TRUE,
                   check.strata = TRUE
                  )
```

```{r}
nfhs <- nfhs %>% 
  mutate(wgt = v005/1000000) %>%  # Turning wewights into decimals
  mutate(strata = as.character(paste(nfhs$state_f, nfhs$place_f, sep = " "))) # Strata based on region and urban/rural

nfhs_design <- nfhs %>%
  as_survey_design(ids = v001, # cluster ids
                   weights = wgt, # weight variable created above
                   strata = strata, # strata
                   nest = TRUE,
                   check.strata = TRUE
                  )
```

Treating single PSUs as 'Certainty': a single-PSU stratum makes no contribution to the variance (for multistage sampling it makes no contribution at that level of sampling). This is an alternative to specifying fpc, and might be useful for compatibility with other software. 

```{r}
options(survey.lonely.psu="certainty")
```

## Regional analysis by zones

### Table with Freq and CIs
```{r}
nfhs_zones_se <- svyby(~antibiotics_f, ~zones_f, design = nfhs_design, svymean, vartype=c("se","ci"))
nfhs_zones_se <- nfhs_zones_se %>%
  dplyr::select(zones_f, antibiotics_fyes, se.antibiotics_fyes, ci_l.antibiotics_fyes, ci_u.antibiotics_fyes) %>% 
  mutate(antibiotics_fyes = antibiotics_fyes *100) %>% 
  mutate(se.antibiotics_fyes = se.antibiotics_fyes *100) %>%
  mutate(ci_l.antibiotics_fyes = ci_l.antibiotics_fyes *100) %>%
  mutate(ci_u.antibiotics_fyes = ci_u.antibiotics_fyes *100)
write_csv(nfhs_zones_se, "nfhs_zones_se.csv")
nfhs_zones_se
```

### Plot prevalence by zone with CIs

```{r}
library(viridis) # Color palette
# Printing mean line
h_line <- paste(sprintf('\u03BC'), paste(round(mean(nfhs_zones_se$antibiotics_fyes), 1), '%', sep = " "), sep = " = ")
h_line

plotnfhs <- ggplot(nfhs_zones_se, aes(x=reorder(zones_f, antibiotics_fyes), y=antibiotics_fyes, colour=zones_f)) + 
    geom_errorbar(aes(ymin=antibiotics_fyes-se.antibiotics_fyes, ymax=antibiotics_fyes+se.antibiotics_fyes), width=.3) +
    geom_point(size= 3)+
    theme_bw()+
    xlab("")+
  ylab("")+
  theme(text = element_text(size=15),
        axis.title.x = element_text(face = "plain", vjust = -.5))+
    scale_y_continuous(
      name="Prevalence of antibiotic treatment (%)", 
      breaks = scales::pretty_breaks(n=12))+
    theme(legend.position="none")+
    coord_flip()+
      geom_hline(yintercept = mean(nfhs_zones_se$antibiotics_fyes), linetype = "dashed", color="black", label) +
      annotate(geom="text", x=1, y=20, label = h_line,
              color="black", size = 4)+
   scale_color_brewer(palette = "Dark2")
plotnfhs
ggsave("nfhs_zones_ci.png", plotnfhs, width=14, height=14, units="cm", dpi=300)
```

## Table with frequency and prevalence by zone and state

```{r}
tbl <- nfhs_design %>% tbl_svysummary(by = antibiotics_f, 
                            include = c(zones_f, state_f),
                            percent = "row",
                            digits = all_categorical() ~ c(1,1))
tbl.flex <- tbl %>% as_flex_table()
tbl.flex
```

### Calculation of SE and 95% CI for the state mean.

```{r}
nfhs_state_se <- svymean(~antibiotics_f, design = nfhs_design, vartype=c("se","ci"))
nfhs_state_se
confint(nfhs_state_se)
```


## Analysis by state

### GT Table State prevalence table with CI

GT table does not allow the calculation of CIs for survey data, so we need to create it first and then add it to the gtsummary table.

```{r}
# Introducing categorical variables names in a vector
tablevars <- c("state_f", "antibiotics_f")

df_result_state <- 
  tibble(variable = tablevars) %>%
  # get the levels of each variable in a new column
  # adding them as a list to allow for different variable classes
  rowwise() %>%
  mutate(
    # level to be used to construct call
    level = unique(nfhs_design$variables[[variable]]) %>% as.list() %>% list(),
    # character version to be merged into table
    label = unique(nfhs_design$variables[[variable]]) %>% as.character() %>% as.list() %>% list()) %>%
  unnest(c(level, label))%>%
  mutate(
    label = unlist(label)
  )


# construct call to svyciprop
df_result_state$svyciprop <-
  map2(
    df_result_state$variable, df_result_state$label,
    function(variable, level) rlang::inject(survey::svyby( ~I(!!rlang::sym(variable) == level), svymean, by = ~antibiotics_f, vartype = "ci", design = nfhs_design))
  )
# The result is a list inside the dataframe that we need unnest and clean.
df_result_state <- df_result_state %>% 
  unnest() %>% 
  dplyr::filter(antibiotics_f == "yes") %>% 
  dplyr::select(!ends_with("FALSE")) %>% 
  dplyr::select(!starts_with("I"))
  
# Merging the results for ci_l
CI95_l <- df_result_state %>% 
  dplyr::select(starts_with("ci_l")) %>% 
  unite(col = "CI_l", sep="", remove = TRUE, na.rm = TRUE)

# Merging the results for ci_u
CI95_u <- df_result_state %>% 
  dplyr::select(starts_with("ci_u")) %>% 
  unite(col = "CI_u", sep="", remove = TRUE, na.rm = TRUE) 

# Binding of the CIs and the variable and label

df_result_state <- cbind(df_result_state, CI95_l, CI95_u)

# Creating a single column with the CI interval
df_result_state <- df_result_state %>% 
  mutate(CI_l = as.numeric(CI_l)) %>% 
  mutate(CI_u = as.numeric(CI_u))

df_result_state$CI_l <- 100*(df_result_state$CI_l)
df_result_state$CI_u <- 100*(df_result_state$CI_u)

# Formatting the CI and selecting the variables
df_result_state <- df_result_state %>% 
  mutate(CI_l = round(CI_l, 2)) %>% 
  mutate(CI_u = round(CI_u, 2)) %>% 
  mutate(CI_95 = as.character(glue('{CI_l} - {CI_u}'))) %>%
  dplyr::select(variable, label, CI_95)

# Construct the GT summary table with CIs
theme_gtsummary_compact(set_theme = TRUE, font_size = NULL) # Compact theme

tbl.state <- 
  nfhs_design %>%
  tbl_svysummary(
    by = antibiotics_f, 
    missing_text = "Missing",
    type = list(all_continuous() ~ "continuous"),
    statistic = list(all_continuous() ~ "{mean} (+/-{sd})",
                     all_categorical() ~ "{n} ({p}%)",
                     all_dichotomous() ~ "{n} ({p}%)"),
    digits = list(all_continuous() ~ c(2, 2),
                  all_categorical() ~ c(2, 2),
                  all_dichotomous() ~ c(2, 2)),
    include = c(      state_f),
    label = c(state_f ~ "State/Union")) %>% 
  modify_header(c(stat_1, stat_2) ~ "**Received antibiotics**<br>N = {n} ({style_percent(p, digits = 1)}%)") %>%
  bold_labels() %>% 
  modify_header(label ~ "") %>%
  # Merge in the CI column
  modify_table_body( 
    ~.x %>%
      left_join(
        df_result_state, 
        by = c("variable", "label")
      )
  ) %>%
  # add a header
  modify_header(CI_95 = "**95% CI**") %>% 
  #hide No antibiotics column
  modify_column_hide(columns = c(stat_1))
tbl.state <- tbl.state %>%  as_flex_table()
tbl.state
```

### Prevalence of antibiotic consumption by state

To create the QGIS Map we need a .csv file with the percentage of antibiotic consumption and the state/zone name.

#### NFHS-4 QGIS .csv
```{r}
ari <- round(svytable(~state_f+ari_f, design = nfhs4_design), 2)
pctage <- round(prop.table(svytable(~state_f+antibiotics_f, nfhs4_design), 1) * 100, 2)
pctage1 <- round(svytable(~state_f+antibiotics_f, design = nfhs4_design), 2)

nfhs4_outcome_by_state <- cbind(ari, pctage1, pctage)
colnames(nfhs4_outcome_by_state) <- c("AriNo", "AriYes","FreqNo", "FreqYes", "PCTNo", "PCTYes")
nfhs4_outcome_by_state 
write.csv(nfhs4_outcome_by_state, "nfhs4_outcome_by_state.csv")
```

#### NFHS-5 QGIS .csv
```{r}
ari <- round(svytable(~state_f+ari_f, design = nfhs5_design), 2)
pctage <- round(prop.table(svytable(~state_f+antibiotics_f, nfhs5_design), 1) * 100, 2)
pctage1 <- round(svytable(~state_f+antibiotics_f, design = nfhs5_design), 2)

nfhs5_outcome_by_state <- cbind(ari, pctage1, pctage)
colnames(nfhs5_outcome_by_state) <- c("AriNo", "AriYes","FreqNo", "FreqYes", "PCTNo", "PCTYes")
nfhs5_outcome_by_state 
write.csv(nfhs5_outcome_by_state, "nfhs5_outcome_by_state.csv")
```
#### NFHS-4 & NFHS-5 merged QGIS .csv
```{r}
ari <- round(svytable(~state_f+ari_f, design = nfhs_design), 2)
pctage <- round(prop.table(svytable(~state_f+antibiotics_f, nfhs_design), 1) * 100, 2)
pctage1 <- round(svytable(~state_f+antibiotics_f, design = nfhs_design), 2)

nfhs_outcome_by_state <- cbind(ari, pctage1, pctage)
colnames(nfhs_outcome_by_state) <- c("AriNo", "AriYes","FreqNo", "FreqYes", "PCTNo", "PCTYes")
nfhs_outcome_by_state 
write.csv(nfhs_outcome_by_state, "nfhs_outcome_by_state.csv")
```

### Prevalence graph with CIs
#### NFHS-4

```{r}
nfhs4_state_se <- svyby(~antibiotics_f, ~state_f, design = nfhs4_design, svymean, vartype=c("se","ci"))
nfhs4_state_se <- nfhs4_state_se %>%
  dplyr::select(state_f, antibiotics_fno, se.antibiotics_fno, ci_l.antibiotics_fno, ci_u.antibiotics_fno, antibiotics_fyes, se.antibiotics_fyes, ci_l.antibiotics_fyes, ci_u.antibiotics_fyes) %>% 
  dplyr::select(state_f, antibiotics_fyes, se.antibiotics_fyes, ci_l.antibiotics_fyes, ci_u.antibiotics_fyes) %>% 
  mutate(antibiotics_fyes = antibiotics_fyes *100) %>% 
  mutate(se.antibiotics_fyes = se.antibiotics_fyes *100) %>%
  mutate(ci_l.antibiotics_fyes = ci_l.antibiotics_fyes *100) %>%
  mutate(ci_u.antibiotics_fyes = ci_u.antibiotics_fyes *100)
write_csv(nfhs4_state_se, "nfhs4_state_se.csv")
nfhs4_state_se
```


```{r}
plotnfhs4 <- ggplot(nfhs4_state_se, aes(x=reorder(state_f, antibiotics_fyes), y=antibiotics_fyes, colour=state_f)) + 
    geom_errorbar(aes(ymin=antibiotics_fyes-se.antibiotics_fyes, ymax=antibiotics_fyes+se.antibiotics_fyes), width=.5) +
    geom_line() +
    coord_flip()+
  theme(legend.position="none")+
    geom_point()
jpeg('plotnfhs4.jpg')
print(plotnfhs4)
dev.off()
```

#### NFHS-5

```{r}
nfhs5_state_se <- svyby(~antibiotics_f, ~state_f, design = nfhs5_design, svymean, vartype=c("se","ci"))
nfhs5_state_se <- nfhs5_state_se %>%
  dplyr::select(state_f, antibiotics_fyes, se.antibiotics_fyes, ci_l.antibiotics_fyes, ci_u.antibiotics_fyes) %>% 
  mutate(antibiotics_fyes = antibiotics_fyes *100) %>% 
  mutate(se.antibiotics_fyes = se.antibiotics_fyes *100) %>%
  mutate(ci_l.antibiotics_fyes = ci_l.antibiotics_fyes *100) %>%
  mutate(ci_u.antibiotics_fyes = ci_u.antibiotics_fyes *100)
write_csv(nfhs5_state_se, "nfhs5_state_se.csv")
nfhs5_state_se
```

```{r}
plotnfhs5 <- ggplot(nfhs5_state_se, aes(x=reorder(state_f, antibiotics_fyes), y=antibiotics_fyes, colour=state_f)) + 
    geom_errorbar(aes(ymin=antibiotics_fyes-se.antibiotics_fyes, ymax=antibiotics_fyes+se.antibiotics_fyes), width=.5) +
    geom_line() +
  theme(legend.position="none")+
  theme(axis.text.y =element_text(size=11))+
  coord_flip()+
  scale_y_discrete(expand=c(0, 0.5)) +
    geom_point()
print(plotnfhs5)    
jpeg('plotnfhs5.jpg')
print(plotnfhs5)
dev.off()
```

#### NFHS-4 & NFHS5 merge

```{r}
nfhs_state_se <- svyby(~antibiotics_f, ~state_f, design = nfhs_design, svymean, vartype=c("se","ci"))
nfhs_state_se <- nfhs_state_se %>%
  dplyr::select(state_f, antibiotics_fyes, se.antibiotics_fyes, ci_l.antibiotics_fyes, ci_u.antibiotics_fyes) %>% 
  mutate(antibiotics_fyes = antibiotics_fyes *100) %>% 
  mutate(se.antibiotics_fyes = se.antibiotics_fyes *100) %>%
  mutate(ci_l.antibiotics_fyes = ci_l.antibiotics_fyes *100) %>%
  mutate(ci_u.antibiotics_fyes = ci_u.antibiotics_fyes *100)
write_csv(nfhs_state_se, "nfhs_state_se.csv")
nfhs_state_se
```

```{r}
h_line <- paste(sprintf('\u03BC'), paste(round(mean(nfhs_state_se$antibiotics_fyes), 1), '%', sep = " "), sep = " = ")
h_line
plotnfhs <- ggplot(nfhs_state_se, aes(x=reorder(state_f, antibiotics_fyes), y=antibiotics_fyes, colour=state_f)) + 
    geom_errorbar(aes(ymin=antibiotics_fyes-se.antibiotics_fyes, ymax=antibiotics_fyes+se.antibiotics_fyes), width=.5) +
    geom_point(size= 2)+
    theme_bw()+
    xlab("")+
  ylab("")+
  theme(text = element_text(size=15),
        axis.title.x = element_text(face = "plain", vjust = -.5))+
    scale_y_continuous(
      breaks = c(0,10,20,30,40,50,60,70,80, 90),
      labels = scales::percent_format(scale = 1, accuracy = 1),
      sec.axis = sec_axis(~., name="Prevalence of antibiotic treatment", 
                          labels = scales::percent_format(scale = 1, accuracy = 1),
                          breaks = c(0,10,20,30,40,50,60,70,80, 90)))+
    theme(legend.position="none")+
    coord_flip()+
      geom_hline(yintercept = mean(nfhs_state_se$antibiotics_fyes), linetype = "dashed", color="black", label) +
      annotate(geom="text", x=2, y=32, label = h_line,
              color="black", size = 4)
plotnfhs
ggsave("nfhs_state_ci.png", plotnfhs, width=23, height=18, units="cm", dpi=300)
```
