---
title: "NFHS Analysis New Table 1"
author: "Hector"
date: '2022-05-27'
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# NFHS Analysis Table 1 weighted

## Objectives

- To create a table containing the Mean (SD/SE) for continuous variables and Frequency (%) for categorical/dichotomous variables

- Table 1 with weighted data containing: outcome variable, sociodemographic variables, household variables, and healthcare variables.

For the weighted data we will use the `gtsummary` package.

### Loading packages

```{r}
knitr::opts_chunk$set(echo = FALSE)

library(tidyverse)   # data management + ggplot2 graphics
library(survey)      # for survey functions
library(srvyr)       # dplyr wrapper for survey package
library(gtsummary)   # wrapper for survey package to produce tables

library(labelled) # Contains the look_for() function
library(epiDisplay) # tab1()
```

## Merging the datasets

```{r}
nfhs4 <- readRDS("nfhs4_ari.Rds")
nfhs5 <- readRDS("nfhs5_ari.Rds")

nfhs4 <- nfhs4 %>% mutate(wave = "NFHS4")
nfhs5 <- nfhs5 %>% mutate(wave = "NFHS5")

nfhs <- bind_rows(nfhs4, nfhs5)
```

## Loading the dataset
```{r}
write_rds(nfhs,"nfhs_ari_all.Rds")
nfhs <- read_rds("nfhs_ari_all.Rds")
```


```{r}
labels <- list(
    variables=list(# Outcome variables
                   antibiotics_f = "Were given antibiotics",
                   
                   # Demographics
                   state_f = "State",
                   wi_f = "Wealth index",
                   religion_f = "Religion",
                   caste_f = "Caste/Tribe",
                   
                   # Child related variables
                   sex_f = "Sex",
                   age = "Age (months)",
                   bord = "Birth order",
                   delivery_g_f = "Place of delivery",
                   stunting_g_f = "Stunting (height/age)",
                   wasting_g_f = "Wasting (weight/height)",
                   
                   # Mother's associated variables
                   m.age = "Mother's age",
                   mageb_g_f = "Maternal age at child birth \u2265 20",
                   m.edu.att_f = "Educational level",
                   smoke_g_f = "Smoke exposure",
                   
                   # Household variables
                   hhsize = "Household size",
                   fuel_g_f = "Type of cooking fuel",
                   water.source_g_f = "Source of drinking water",
                   toilet_g_f = "Toilet facility",
                   handwash.soap_f = "Soap for handwashing",
                   media_f = "Media accessibility",
                   bpl_f = "Below Poverty Line card",
                   
                   # Treatment related variables
                   source_g1_f = "Source of treatment",
                   days.after_g_f = "Days after treatment",
                   eat_g_f = "Amount given to eat",
                   drink_g_f = "Amount given to drink",
                   
                   # Health care related variables
                   access = "Problems accessing healthcare",
                   distance_f = "Distance to health facility",
                   visit3mo_f = "Health worker visit in last 3 months",
                   insurance_f = "Covered by health insurance",
                   healthcard_f = "Has health card",
                   
                   # Vaccination
                   fimm_f = "Fully immunized",
                   dpt3 = "DPT vaccine (3 doses)",
                   polio3 = "Polio (3 doses)",
                   bcg_f = "BCG vaccine",
                   measles_f = "Measles vaccine",
                   
                   icds_f = "Anganwadi or ICDS benefits",
                   parasites_f = "Drugs for intestinal parasites (last 6 months)",
                   vitA_f = "Vitamin A supplementation (last 6 months)",
                   iron_f = "Iron supplementation (last 7 days)"))
```



Trial table to modify the rendering and lay out of the final table

```{r}
theme_gtsummary_compact(set_theme = TRUE, font_size = NULL)
table.trial <- nfhs %>%
  mutate_if(is.factor,
            fct_explicit_na,
            na_level = "Missing") %>%  ### Setting missing variables as a category to obtain percentage of missing values
  tbl_summary(
    by = place_f, 
    missing_text = "Missing",
    type = list(all_continuous() ~ "continuous"),
    statistic = list(all_continuous() ~ "{mean} (+/-{sd})",
                     all_categorical() ~ "{n} ({p}%) ",
                     all_dichotomous() ~ "{n} ({p}%) "),
    digits = list(all_continuous() ~ c(2, 2),
                  all_categorical() ~ c(0, 2),
                  all_dichotomous() ~ c(2, 2)),
    include = c(antibiotics_f,
                age,
                sex_f,
                stunting_g_f,
                icds_f),
    label = c(antibiotics_f ~ "Were given antibiotics",
              sex_f ~ "Sex",
              age ~ "Age (months)",
              stunting_g_f ~ "Stunting (height/age)",
              icds_f ~ "Anganwadi/ICDS benefits")) %>% 
  add_overall() %>% 
  modify_header(c(stat_1, stat_2) ~ "**{level}**<br>N = {n} ({style_percent(p, digits = 1)}%)") %>%
  bold_labels() %>% 
  modify_header(label ~ "") %>%
  modify_footnote(
    all_stat_cols() ~ "Mean (SD) or Frequency (%)")
  

table1_gt <- as_gt(table.trial)
table1_gt
```
## Weights and survey design

```{r}
nfhs <- nfhs %>% 
  mutate(wgt = v005/1000000) %>%  # Turning weights into decimals
  mutate(strata = as.character(paste(nfhs$state_f, nfhs$place_f, sep = " "))) # Strata based on region and urban/rural

nfhs_design <- nfhs %>% 
  mutate_if(is.factor,
            fct_explicit_na,
            na_level = "Missing") %>% # To calculate the % of missing values we need to include the NA's as a category
  as_survey_design(ids = v001, # cluster ids
                   weights = wgt, # weight variable created above
                   strata = strata, # strata
                   nest = TRUE,
                   check.strata = TRUE)
```

Treating single PSUs as 'Certainty':

Certainty: a single-PSU stratum makes no contribution to the variance (for multistage sampling it makes no contribution at that level of sampling). This is an alternative to specifying fpc, and might be useful for compatibility with other software. 

```{r}
options(survey.lonely.psu="certainty")
```

## Table 1. Descriptive analysis by urban/rural.

```{r}
theme_gtsummary_compact(set_theme = TRUE, font_size = NULL) # Compact theme

table1 <- nfhs_design %>%
  tbl_svysummary(
    by = place_f, 
    missing_text = "Missing",
    type = list(all_continuous() ~ "continuous",
                access ~ "continuous"),
    statistic = list(all_continuous() ~ "{mean} (+/-{sd})",
                     all_categorical() ~ "{n} ({p}%)",
                     all_dichotomous() ~ "{n} ({p}%)"),
    digits = list(all_continuous() ~ c(1, 1),
                  all_categorical() ~ c(0, 1),
                  all_dichotomous() ~ c(0, 1)),
    include = c(antibiotics_f,
                   
# Demographics
wi_f,
religion_f,
caste_f,

# Mother's associated variables
m.age,
m.edu.att_f,

            
# Household variables
hhsize,
died_f,
fuel_g_f,
water.source_g_f,
toilet_g_f,
handwash.soap_f,
media_f,
bpl_f,
smoke_g_f,

# Child related variables
sex_f,
age,
bord,
delivery_g_f,
stunting_g_f,
wasting_g_f,
                   
# Health care related variables
access,
visit3mo_f,
insurance_f,
healthcard_f,
fimm_f,
icds_f,
parasites_f,
vitA_f,
iron_f,

# Treatment related variables
source_g1_f,
days.after_g_f,
eat_g_f,
drink_g_f),

    label = c(
# Outcome variables
antibiotics_f ~ "Were given antibiotics",

# Demographics
wi_f ~ "Wealth index",
religion_f ~ "Religion",
caste_f ~ "Caste/Tribe",

# Mother's associated variables
m.age ~ "Mother's age (years)",
m.edu.att_f ~ "Educational level",
                   
# Child related variables
sex_f ~ "Sex",
age ~ "Age (months)",
bord ~ "Birth order",
delivery_g_f ~ "Place of delivery",
stunting_g_f ~ "Stunting (height/age)",
wasting_g_f ~ "Wasting (weight/height)",
                   
# Household variables
hhsize ~ "Household size",
died_f ~ "Any previous children deceased",
fuel_g_f ~ "Type of cooking fuel",
water.source_g_f ~ "Source of drinking water",
toilet_g_f ~ "Toilet facility",
handwash.soap_f ~ "Soap for handwashing",
media_f ~ "Media accessibility",
bpl_f ~ "Below Poverty Line card",
smoke_g_f ~ "Smoke exposure",
                   
# Health care related variables
access ~ "Problems accessing healthcare",
visit3mo_f ~ "Health worker visit in last 3 months",
insurance_f ~ "Covered by health insurance",
healthcard_f ~ "Has health card",
fimm_f ~ "Fully immunized",
icds_f ~ "Anganwadi or ICDS benefits",
parasites_f ~ "Drugs for intestinal parasites (last 6 months)",
vitA_f ~ "Vitamin A supplementation (last 6 months)",
iron_f ~ "Iron supplementation (last 7 days)",

# Treatment related variables
source_g1_f ~ "Source of treatment",
days.after_g_f ~ "Days after treatment",
eat_g_f ~ "Amount given to eat",
drink_g_f ~ "Amount given to drink")) %>% 
  add_overall() %>% 
  modify_header(c(stat_1, stat_2) ~ "**{level}**<br>N = {n} ({style_percent(p, digits = 1)}%)") %>%
  bold_labels() %>% 
  modify_header(label ~ "") %>%
  modify_footnote(
    all_stat_cols() ~ "Mean (SD) or Frequency (%)")

table1_flex <- as_flex_table(table1) # Flex format is easier to export in a word document
table1_flex
```

### Calcualting SE of continuous variables

GT summary does not offer a direct option for calculating SE, instead of the SD, so we calculate them here and change them manually.

```{r}

round(svymean(~m.age, vartype = c("mean", "se"), design = nfhs_design), 1)
svyby(~antibiotics_f, by = ~wave, design = nfhs_design, svymean, vartype=c("mean","se", "ci", "count"))

svymean(~hhsize, vartype = c("mean", "se"), design = nfhs_design)
svyby(~hhsize, by = ~place_f, design = nfhs_design, svymean, vartype=c("mean","se"))

svymean(~age, vartype = c("mean", "se"), design = nfhs_design)
svyby(~age, by = ~place_f, design = nfhs_design, svymean, vartype=c("mean","se"))

svymean(~bord, vartype = c("mean", "se"), design = nfhs_design)
svyby(~bord, by = ~place_f, design = nfhs_design, svymean, vartype=c("mean","se"))

svymean(~access, vartype = c("mean", "se"), design = nfhs_design)
svyby(~access, by = ~place_f, design = nfhs_design, svymean, vartype=c("mean","se"))

svymean(~days.after, vartype = c("mean", "se"), na.rm = TRUE,design = nfhs_design)
svyby(~days.after, by = ~place_f, na.rm = TRUE, design = nfhs_design, svymean, vartype=c("mean","se"))

```


## Table 1. Descriptive analysis by wave.

Exploring the distribution of the outcome by waves.

```{r}
table1 <- nfhs_design %>%
  tbl_svysummary(
    by = wave, 
    missing_text = "Missing",
    type = list(all_continuous() ~ "continuous"),
    statistic = list(all_continuous() ~ "{mean} (+/-{sd})",
                     all_categorical() ~ "{n} ({p}%)",
                     all_dichotomous() ~ "{n} ({p}%)"),
    digits = list(all_continuous() ~ c(1, 1),
                  all_categorical() ~ c(0, 1),
                  all_dichotomous() ~ c(0, 1)),
    include = c(antibiotics_f))
                table1
```



--------------------------
### List of variables

To easily access (copy and paste) all the variables of interested I kept all the variables we decided to include in the analysis here:

#### Outcome
antibiotics_f, 
                   
#### Demographics
state_f,
wi_f,
religion_f,
caste_f,
                   
#### Child related variables
sex_f,
age,
bord,
delivery_g_f,
stunting_g_f,
wasting_g_f,
                   
#### Mother's associated variables
m.age,
mageb_g_f,
m.edu.att_f,
smoke_g_f,
                   
#### Household variables
hhsize,
fuel_g_f,
water.source_g_f,
toilet_g_f,
handwash.soap_f,
media_f,
bpl_f,
                   
#### Treatment related variables
source_g1_f,
days.after_g_f,
eat_g_f,
drink_g_f,
                   
#### Health care related variables
access,
distance_f,
visit3mo_f,
insurance_f,
healthcard_f,
                   
#### Vaccination
fimm_f,
dpt3,
polio3,
bcg_f,
measles_f,
                   
icds_f,
parasites_f,
vitA_f,
iron_f

------------------------------------------------

#### Outcome variables
antibiotics_f ~ "Were given antibiotics",

#### Demographics
state_f ~ "State",
wi_f ~ "Wealth index",
religion_f ~ "Religion",
caste_f ~ "Caste/Tribe",
                   
#### sex_f ~ "Sex",
age ~ "Age (months)",
bord ~ "Birth order",
delivery_g_f ~ "Place of delivery",
stunting_g_f ~ "Stunting (height/age)",
wasting_g_f ~ "Wasting (weight/height)",
                   
#### Mother's associated variables
m.age ~ "Mother's age",
mageb_g_f ~ "Maternal age at child birth \u2265 20",
m.edu.att_f ~ "Educational level",
smoke_g_f ~ "Smoke exposure",
                   
#### Household variables
hhsize ~ "Household size",
fuel_g_f ~ "Type of cooking fuel",
water.source_g_f ~ "Source of drinking water",
toilet_g_f ~ "Toilet facility",
handwash.soap_f ~ "Soap for handwashing",
media_f ~ "Media accessibility",
bpl_f ~ "Below Poverty Line card",
                   
#### Treatment related variables
source_g1_f ~ "Source of treatment",
days.after_g_f ~ "Days after treatment",
eat_g_f ~ "Amount given to eat",
drink_g_f ~ "Amount given to drink",
                   
#### Health care related variables
access ~ "Problems accessing healthcare",
distance_f ~ "Distance to health facility",
visit3mo_f ~ "Health worker visit in last 3 months",
insurance_f ~ "Covered by health insurance",
healthcard_f ~ "Has health card",
                   
#### Vaccination
fimm_f ~ "Fully immunized",
dpt3 ~ "DPT vaccine (3 doses)",
polio3 ~ "Polio (3 doses)",
bcg_f ~ "BCG vaccine",
measles_f ~ "Measles vaccine",
                   
icds_f ~ "Anganwadi or ICDS benefits",
parasites_f ~ "Drugs for intestinal parasites (last 6 months)",
vitA_f ~ "Vitamin A supplementation (last 6 months)",
iron_f ~ "Iron supplementation (last 7 days)"

