---
title: "Logistic Regression"
author: "Hector"
date: '2022-06-22'
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Logistic Regression Analysis

## Objectives

- To identify and quantify the risk differences (RD) of the selected predictor variables and antibiotic consumption in U3 children with ARI.

- To progressively create regression models by groups of variables adjusting for factors more proximal to the outcome.

- To create a gtsummary table containing the the frequency of antibiotic consumption for each variable and the estimations from the models.

```{r}
library(tidyverse)   # data management + ggplot2 graphics
library(survey)      # for survey functions
library(srvyr)       # dplyr wrapper for survey package
library(gtsummary)   # wrapper for survey package to produce tables

library(labelled) # Contains the look_for() function
library(epiDisplay) # tab1()
library(scales) # percent() 
library(glue) # glue()
library(gt) # gt table 
library(modelsummary) # summary of model statistics side by side

# Packages for logistic regression model marginal effect measurements
library(margins) # devtools::install_github("tzoltak/prediction") Updated to handle NA values
library(prediction) #devtools::install_github("tzoltak/margins") Updated to handle NA values


```

## Merging the datasets

```{r}
nfhs4 <- readRDS("nfhs4_ari.Rds")
nfhs5 <- readRDS("nfhs5_ari.Rds")

nfhs4 <- nfhs4 %>% mutate(wave = "NFHS4")
nfhs5 <- nfhs5 %>% mutate(wave = "NFHS5")

nfhs <- bind_rows(nfhs4, nfhs5)

```

## Loading the dataset
```{r}
write_rds(nfhs,"nfhs_ari_all.Rds")
nfhs <- read_rds("nfhs_ari_all.Rds")
```


## Weights and survey design

```{r}
nfhs$caste_f <- relevel(nfhs$caste_f, ref = "None") #Changing reference of caste category to None

nfhs <- nfhs %>% 
  mutate(wgt = v005/1000000) %>%  # Turning weights into decimals
  mutate(strata = as.character(paste(nfhs$state_f, nfhs$place_f, sep = " "))) # Strata based on region and urban/rural

nfhs_design <- nfhs %>%
  as_survey_design(ids = v001, # cluster ids
                   weights = wgt, # weight variable created above
                   strata = strata, # strata
                   nest = TRUE,
                   check.strata = TRUE
                  )
```

Treating single PSUs as 'Certainty': a single-PSU stratum makes no contribution to the variance (for multistage sampling it makes no contribution at that level of sampling). This is an alternative to specifying fpc, and might be useful for compatibility with other software. 

```{r}
options(survey.lonely.psu="certainty")
```

## Regression models by groups of variables

### Demographics

```{r}
theme_gtsummary_compact(set_theme = TRUE, font_size = NULL) # Compact theme

demographics.model <- svyglm(antibiotics_f ~ 
# Demographics
place_f+
wi_f +
religion_f +
caste_f+
m.age+
m.edu.att_f,

 family = quasibinomial(link = 'logit'), design = nfhs_design)
a<-summary(margins(demographics.model))
a

tbl.demog <- margins(demographics.model, design = nfhs_design) %>%
  tbl_regression() %>% 
  modify_fmt_fun(update = estimate ~ label_percent(accuracy = 0.1)) %>% 
  #modify_column_hide(columns = c(p.value)) %>% 
  modify_header(estimate ~ "**RD**") %>% 
  bold_p(t = 0.05)

# Changing the format of the CI
tbl.demog$table_body$conf.low <- round(tbl.demog$table_body$conf.low*100,1)
tbl.demog$table_body$conf.high <-round(tbl.demog$table_body$conf.high*100,1)
tbl.demog$table_body$ci <-as.character(glue('{tbl.demog$table_body$conf.low}, {tbl.demog$table_body$conf.high}'))

tbl.demog_flex <- as_flex_table(tbl.demog) # Flex format is easier to export in a word document
tbl.demog_flex
```


### Household

```{r}
hh.model <- svyglm(antibiotics_f ~ 
# Demographics

place_f+
wi_f +
religion_f +
caste_f+

m.age+
m.edu.att_f+
# Household variables
hhsize +
died_f+
fuel_g_f +
water.source_g_f +
toilet_g_f +
handwash.soap_f +
media_f +
bpl_f +
smoke_g_f,
family = quasibinomial(link = 'logit'), design = nfhs_design)

tbl.hh <- margins(hh.model, design = nfhs_design) %>%
  tbl_regression() %>% 
  modify_fmt_fun(update = estimate ~ label_percent(accuracy = 0.1)) %>% 
  #modify_column_hide(columns = c(p.value)) %>% 
  modify_header(estimate ~ "**RD**") %>% 
  bold_p(t = 0.05)

# Changing the format of the CI
tbl.hh$table_body$conf.low <- round(tbl.hh$table_body$conf.low*100,1)
tbl.hh$table_body$conf.high <-round(tbl.hh$table_body$conf.high*100,1)
tbl.hh$table_body$ci <-as.character(glue('{tbl.hh$table_body$conf.low}, {tbl.hh$table_body$conf.high}'))

tbl.hh_flex <- as_flex_table(tbl.hh) # Flex format is easier to export in a word document
tbl.hh_flex
```

### Child related
```{r}
child.model <- svyglm(antibiotics_f ~ 
# Demographics

place_f+
wi_f +
religion_f +
caste_f+

m.age+
m.edu.att_f+
# Household variables
hhsize +
died_f+
fuel_g_f +
water.source_g_f +
toilet_g_f +
handwash.soap_f +
media_f +
bpl_f +
smoke_g_f+
# Child variables
sex_f +
age +
bord +
delivery_g_f +
stunting_g_f +
wasting_g_f+
healthcard_f +
fimm_f, 

family = quasibinomial(link = 'logit'), design = nfhs_design)

tbl.child <- margins(child.model, design = nfhs_design) %>%
  tbl_regression() %>% 
  modify_fmt_fun(update = estimate ~ label_percent(accuracy = 0.1)) %>% 
  #modify_column_hide(columns = c(p.value)) %>% 
  modify_header(estimate ~ "**RD**") %>% 
  bold_p(t = 0.05)

# Changing the format of the CI
tbl.child$table_body$conf.low <- round(tbl.child$table_body$conf.low*100,1)
tbl.child$table_body$conf.high <-round(tbl.child$table_body$conf.high*100,1)
tbl.child$table_body$ci <-as.character(glue('{tbl.child$table_body$conf.low}, {tbl.child$table_body$conf.high}'))

tbl.child_flex <- as_flex_table(tbl.child) # Flex format is easier to export in a word document
tbl.child_flex
```
### Healthcare

```{r}
healthcare.model <- svyglm(antibiotics_f ~ 
# Demographics

# Demographics

place_f+
wi_f +
religion_f +
caste_f+

m.age+
m.edu.att_f+
# Household variables
hhsize +
died_f+
fuel_g_f +
water.source_g_f +
toilet_g_f +
handwash.soap_f +
media_f +
bpl_f +
smoke_g_f+
# Child variables
sex_f +
age +
bord +
delivery_g_f +
stunting_g_f +
wasting_g_f+ 
# Health care related variables
access +
visit3mo_f +
insurance_f +
healthcard_f +
fimm_f +
icds_f +
parasites_f +
vitA_f +
iron_f +
source_g1_f, na.action = na.omit,
family = quasibinomial(link = 'logit'), design = nfhs_design)

tbl.hc <- margins(healthcare.model, design = nfhs_design) %>%
  tbl_regression() %>% 
  modify_fmt_fun(update = estimate ~ label_percent(accuracy = 0.1)) %>% 
  #modify_column_hide(columns = c(p.value)) %>% 
  modify_header(estimate ~ "**RD**") %>% 
  bold_p(t = 0.05)

# Changing the format of the CI
tbl.hc$table_body$conf.low <- round(tbl.hc$table_body$conf.low*100,1)
tbl.hc$table_body$conf.high <-round(tbl.hc$table_body$conf.high*100,1)
tbl.hc$table_body$ci <-as.character(glue('{tbl.hc$table_body$conf.low}, {tbl.hc$table_body$conf.high}'))

tbl.hc_flex <- as_flex_table(tbl.hc) # Flex format is easier to export in a word document
tbl.hc_flex

```

### Merging all models

```{r}
merge_nfhs <- tbl_merge(list(tbl.demog, tbl.hh, tbl.child,  tbl.hc), tab_spanner = F)
merge_nfhs %>%  as_flex_table()
merge_nfhs
```

### Multimodel 

To visualize the number of observations that were used for each model we use `modelsummary()` function that creates also fitness tests not relevant for our model.

```{r}
modelsummary(list(demographics.model, hh.model, child.model, healthcare.model))
```

