---
title: "NFHS4 HH cleaning"
author: "Hector"
date: '2022-05-18'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# NFHS4 Household Data cleaning

## Objectives

-   Input the household dataset from .DTA file.

-   Create a .R dataset easier and quicker to handle that contains the key values for the merging with the birth record dataset and the variables that we are interested in merging.


### Loading the dataset

First of all we will load the necessary packages:

```{r}
library(tidyverse)
library(labelled) # Contains the look_for() function
library(epiDisplay) # tab1()
```


Pushing a bit the RAM memory by doing garbage collection (RAM memory cleaning) and raising the memory.limit:
```{r}
gc()
memory.limit()
memory.limit(size = 60000)
```

Then we will proceed to load the NFHS dataset onto R.

```{r}
library(haven)
 #hhsurvey <- read_dta("IAHR74FL.DTA")
```

### Save as R data file, for faster loading.

```{r}
# saveRDS(hhsurvey, file = "IAHR74FL.Rds")
hhsurvey <- readRDS(file = "IAHR74FL.Rds")
```

Selecting only the variables necessary for merging and washing hands:

 63  hv230a   place where household members wash their hands dbl+lbl  [1] observed                          
                                                                      [2] not observed: not in dwelling     
                                                                      [3] not observed: no permission to see
                                                                      [4] not observed: other reason        
 64  hv230b   presence of water at hand washing place        dbl+lbl  [0] water not available               
                                                                      [1] water is available 
```{r}
tab1(hhsurvey$hv252)
```

```{r}
hhsurvey_small <- hhsurvey %>% dplyr::select(hhid, hv000, hv001, hv002, hv003, hv004, hv005, hv230a, hv230b, hv232, hv232b, hv232y, hv252, sh58)
```


Saving the resulted dataset:

```{r}
saveRDS(hhsurvey_small, file = "HHsurvey_small_merge.Rds")
```
